%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Web/Digital Marketing Analyst - Student Worker} % Job title
    {UCM - Integrated Marketing \& Communications.} % Organisation
    {Warrensburg, MO, USA} % Location
    {Aug 2023 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managing content for UCM’s website via OmniCMS, leading to a 15\% increase in user engagement.}
        \item {Utilizing Google Analytics 4, Looker Studio, and Matomo to analyze web traffic, resulting in a 10\% improvement in user retention and a 15\% decrease in bounce rate.}
        \item {Translating web analytics into Google Sheets visuals, improving stakeholder comprehension.}
        \item {Working with Matomo, Google Analytics, Looker Studio, and Google Sheets.}
        % \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation skills.}
      \end{cvitems}
    }
    % cmi -associate
    \cventry
    {Associate Engineer} % Job title
    {CoMakeIT Software Pvt Ltd. (Xebia Product Engineering)} % Organisation
    {Hyderabad, TS, India} % Location
    {July 2022 – May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Played a Key role in an application migration from Heroku to Aws Cloud which included the migration of 7 applications, 5 databases, and multiple other AWS‐managed services such as Redis, elastic search, and Memcache.}
        \item {Designed an automation tool that simplified the construction of user‐defined architecture, leading to a 50\% decrease in manual setup duration.}
          \item {Integrated and managed over 20 AWS resources, utilizing tools like Papertrail for real‐time logging and AWS CDK to implement infrastructure‐as‐code, resulting in 30\% faster deployment times.}
            \item {Leveraged Spring Boot, PostgreSQL, Bash, and Linux Administration to drive R\&D efforts, leading to the successful launch of 2 major projects.}
         % \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation skills.}
        % \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation skills.}
      \end{cvitems}
    }
    % cmi intern
     \cventry
    {Engineer Intern} % Job title
    {} % Organisation
    {} % Location
    {Sep 2021 – June 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a Banking Project using J2EE and JavaScript.}
        \item {Integrated DevOps tools: Docker, Jenkins, Ansible, and Terraform, boosting deployment efficiency by 40\%.}
         \item {Used Spring Boot, PostgreSQL, React, Bash, and Linux Administration.}
        % \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation skills.}
        % \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation skills.}
      \end{cvitems}
    }   
        % synergina intern
     \cventry
    {Full-Stack Developer Intern} % Job title
    {Synergina Pvt Ltd.} % Organisation
    {Hyderabad, TS, India} % Location
    {Nov 2020 – Feb 2021.} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spearheaded the development of a product tailored specifically for small manufacturers and retailers, driving a 40\% increase in sales revenue and market penetration.}
        \item {Contributed to an ERP system, enhancing organizational efficiency.}
         \item {Initiated a project optimizing employee task management, boosting productivity.}
          \item {Used Node.js, MongoDB (Mongoose), and RESTful API.}
        % \item {\textbf{Technical Skills:} Matomo, Google Analytics, Looker Studio, Google Sheets.}
        % \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation skills.}
      \end{cvitems}
    }
     % kirg intern
     \cventry
    {Back End Developer Intern} % Job title
    {Kirg Technologies.} % Organisation
    {Hyderabad, TS, India} % Location
    {July 2020 – Sep 2020.} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on a project that focuses on college student's academics.}
        \item  {That project focuses on digitalizing all the manual work done in colleges.}
        \item {Used PHP, SQL(MySQL), and WordPress.}
        % \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation skills.}
      \end{cvitems}
    }
     % cmr intern
     \cventry
    {Undergardaute Developer} % Job title
    {CMR Institute of Technology.} % Organisation
    {Hyderabad, TS, India} % Location
    {Sep 2019 – June 2020.} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented Grievance software, streamlining the communication process for 2000+ students to submit queries directly to stakeholders, reducing response time by 50\% and improving overall student satisfaction.}
        \item {Designed and developed colleges' leave management system.}
        \item {Used PHP, SQL (MySQL), and other frontend technologies.}
        % \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation skills.}
      \end{cvitems}
    }



\end{cventries}
