%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cvproject
    {\textbf{Hospital Appointment Booking System.}} % Organisation
    {}
    {}
    {}
    {
      \begin{cvitems} % Description(s) of project
        \item {Aiming to optimize appointment bookings in healthcare settings using Django and MongoDB.
}
        \item {Crafting an intuitive interface with Django for appointment functionalities}
        \item {Leveraging MongoDB for efficient data handling and rapid retrieval.}
               \item {Implementing real-time slot checks to mitigate scheduling overlaps.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cvproject
    {\textbf{Django Online MarketPlace}} % Organisation
    {}
    {}
    {}
    {
      \begin{cvitems} % Description(s) of project
        \item {Designing a user-centric e-commerce interface with Django for streamlined shopping and checkout processes.}
        \item {Employing MongoDB for robust product catalog storage and swift transaction handling.}
        \item {Integrating real-time inventory updates to ensure product availability and reduce order discrepancies.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cvproject
    {\textbf{GRIEVANCE SYSTEM.}} % Organisation
    {}
    {}
    {}
    {
      \begin{cvitems} % Description(s) of project
        \item {Streamlined query and complaint process in bustling academic and professional environments by implementing a user-friendly digital platform.}
        \item {The submitted query would be only visible to the admin who has the authority to solve queries. Made it using PHP and MySQL.}
        % \item {Specific case studies were traced back to trends seen in the UK and how they affected the GDP and IMR.}
      \end{cvitems}
    }


%---------------------------------------------------------
  % \cvproject
  %    {\textbf{VISUALIZING EARNING BASED ON COLLEGE MAJORS.}} % Organisation
  %   {}
  %   {}
  %   {}
  %   {
  %     \begin{cvitems} % Description(s) of project
  %       \item {Worked with a dataset on the job outcomes of students who graduated from college between 2010 and 2012.}
  %       \item {The original data on job outcomes was released by American Community Survey, which conducts surveys and aggregates the data.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  \cvproject
     {\textbf{YELP - WEB SCRAPER (PYTHON).}} % Organisation
    {}
    {}
    {}
    {
      \begin{cvitems} % Description(s) of project
        \item {A user-friendly web scrapper provides business data of a particular location when the the location parameter is given.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
